--- 
title: "MSc Thesis"
shorttitle: "MSc Thesis"

author: Michael McCarthy^[University of Calgary, michael.mccarthy@ucalgary.ca]

date: "`r Sys.Date()`"

site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: ["`r rbbt::bbt_write_bib('references.json', overwrite = TRUE)`", "r-packages.bib"]
biblio-style: "apa.csl"
link-citations: yes

github-repo: mccarthy-m-g/msc-thesis

favicon: www/favicon.ico
cover-image: 
description: "Michael McCarthy's work-in-progress MSc thesis."
---
```{r include=FALSE, cache=FALSE}
set.seed(1014)
options(digits = 3)

###############################################################################
## setup
###############################################################################
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = TRUE,
  fig.retina = 0.8, # figures are either vectors or 300 dpi diagrams
  dpi = 300,
  out.width = "70%",
  fig.align = 'center',
  fig.width = 6,
  fig.asp = 0.618,  # 1 / phi
  fig.show = "hold",
  eval.after = 'fig.cap' # so captions can use link to demos
)

options(dplyr.print_min = 6,
        dplyr.print_max = 6,
        knitr.graphics.auto_pdf = TRUE)
```

```{r setup, include=FALSE}
renv::snapshot()
```

# Welcome {-}

This is the online, work-in-progress, version of my MSC thesis.

<!--chapter:end:index.Rmd-->

```{r include=FALSE, cache=FALSE}
set.seed(1014)
options(digits = 3)

###############################################################################
## setup
###############################################################################
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = TRUE,
  fig.retina = 0.8, # figures are either vectors or 300 dpi diagrams
  dpi = 300,
  out.width = "70%",
  fig.align = 'center',
  fig.width = 6,
  fig.asp = 0.618,  # 1 / phi
  fig.show = "hold",
  eval.after = 'fig.cap' # so captions can use link to demos
)

options(dplyr.print_min = 6,
        dplyr.print_max = 6,
        knitr.graphics.auto_pdf = TRUE)
```
# Preface {#preface}

## Acknowledgments

A big thank you to everyone who has supported me on this journey.

```{r, echo=FALSE}
# code taken from: https://github.com/hadley/mastering-shiny/blob/master/introduction.Rmd
library(magrittr)
contribs_all_json <- gh::gh("/repos/:owner/:repo/contributors",
  owner = "mccarthy-m-g",
  repo = "bookdown-thesis-template",
  .limit = Inf
)
contribs_all <- tibble::tibble(
  login = contribs_all_json %>% purrr::map_chr("login"),
  n = contribs_all_json %>% purrr::map_int("contributions")
)
contribs_old <- readr::read_csv("contributors.csv", col_types = list())
contribs_new <- contribs_all %>% dplyr::anti_join(contribs_old, by = "login")
# Get info for new contributors
needed_json <- purrr::map(
  contribs_new$login, 
  ~ gh::gh("/users/:username", username = .x)
)
info_new <- tibble::tibble(
  login = contribs_new$login,
  name = purrr::map_chr(needed_json, "name", .default = NA),
  blog = purrr::map_chr(needed_json, "blog", .default = NA)
)
info_old <- contribs_old %>% dplyr::select(login, name, blog)
info_all <- dplyr::bind_rows(info_old, info_new)
contribs_all <- contribs_all %>% 
  dplyr::left_join(info_all, by = "login") %>% 
  dplyr::arrange(login)
readr::write_csv(contribs_all, "contributors.csv")
```

```{r, echo=FALSE, results = "asis", message = FALSE}
# code modified from: https://github.com/hadley/mastering-shiny/blob/master/introduction.Rmd
contributors <- read.csv("contributors.csv", stringsAsFactors = FALSE)
contributors <- contributors %>% 
  dplyr::filter(login != "mccarthy-m-g") %>% 
  dplyr::mutate(
    login = paste0("\\@", login),
    desc = ifelse(is.na(name), login, paste0(name, " (", login, ")"))
  )
if (nrow(contributors) != 0) {
  cat("This thesis was written in the open, and many people have contributed fixes and improvements. A big thank you to all ", nrow(contributors), " people who contributed via GitHub pull requests (in alphabetical order by username): ", sep = "")
  cat(paste0(contributors$desc, collapse = ", "))
  cat(".\n")
}
```

## Colophon

This thesis was written in [RStudio](http://www.rstudio.com/ide/) using [bookdown](http://bookdown.org/). The online version of this thesis is available at https://mccarthymg-msc-thesis.netlify.app/. It is hosted with [netlify](http://netlify.com/), and is automatically updated after every commit by [GitHub Actions](https://help.github.com/en/actions). The complete source is available at https://github.com/mccarthy-m-g/msc-thesis.

This version of the template was built with `r R.version.string` and the following packages:

```{r, echo=FALSE, results="asis", warning=FALSE, message=FALSE}
# read renv.lock
renvLock <- jsonlite::read_json("renv.lock")
# write R packages from renv.lock to r-packages.bib
knitr::write_bib(names(renvLock$Packages), "r-packages.bib")
# get location of package versions and sources
pkg_version <- paste0("renvLock$Packages$", names(renvLock$Packages), "$Version")
pkg_source <- paste0("renvLock$Packages$", names(renvLock$Packages), "$Repository")

# create tibble of packages, their versions, and their source
df <- tibble::tibble(
  package = names(renvLock$Packages),
  version = sapply(pkg_version, function(x) eval(parse(text = x))),
  source = sapply(pkg_source, function(x) eval(parse(text = x)))
)
knitr::kable(df, format = "markdown")
```

```{r, echo=FALSE}
# code taken from: https://github.com/hadley/mastering-shiny/blob/master/introduction.Rmd
ruler <- function(width = getOption("width")) {
  x <- seq_len(width)
  y <- dplyr::case_when(
    x %% 10 == 0 ~ as.character((x %/% 10) %% 10),
    x %% 5 == 0  ~ "+",
    TRUE         ~ "-"
  )
  cat(y, "\n", sep = "")
  cat(x %% 10, "\n", sep = "")
}
```
```{r, echo=FALSE, include = FALSE}
ruler()
```

<!--chapter:end:preface.Rmd-->

```{r include=FALSE, cache=FALSE}
set.seed(1014)
options(digits = 3)

###############################################################################
## setup
###############################################################################
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = TRUE,
  fig.retina = 0.8, # figures are either vectors or 300 dpi diagrams
  dpi = 300,
  out.width = "70%",
  fig.align = 'center',
  fig.width = 6,
  fig.asp = 0.618,  # 1 / phi
  fig.show = "hold",
  eval.after = 'fig.cap' # so captions can use link to demos
)

options(dplyr.print_min = 6,
        dplyr.print_max = 6,
        knitr.graphics.auto_pdf = TRUE)
```
# (PART) Research Proposal {-}

# CGS-M

@holbourn_MechanicsHeadInjuries_1943

<!--chapter:end:research-proposal.Rmd-->

```{r include=FALSE, cache=FALSE}
set.seed(1014)
options(digits = 3)

###############################################################################
## setup
###############################################################################
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = TRUE,
  fig.retina = 0.8, # figures are either vectors or 300 dpi diagrams
  dpi = 300,
  out.width = "70%",
  fig.align = 'center',
  fig.width = 6,
  fig.asp = 0.618,  # 1 / phi
  fig.show = "hold",
  eval.after = 'fig.cap' # so captions can use link to demos
)

options(dplyr.print_min = 6,
        dplyr.print_max = 6,
        knitr.graphics.auto_pdf = TRUE)
```
# (PART) Example Chapters {-}

# Introduction


<!--chapter:end:introduction.Rmd-->

```{r include=FALSE, cache=FALSE}
set.seed(1014)
options(digits = 3)

###############################################################################
## setup
###############################################################################
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = TRUE,
  fig.retina = 0.8, # figures are either vectors or 300 dpi diagrams
  dpi = 300,
  out.width = "70%",
  fig.align = 'center',
  fig.width = 6,
  fig.asp = 0.618,  # 1 / phi
  fig.show = "hold",
  eval.after = 'fig.cap' # so captions can use link to demos
)

options(dplyr.print_min = 6,
        dplyr.print_max = 6,
        knitr.graphics.auto_pdf = TRUE)
```
# Methodology


<!--chapter:end:methodology.Rmd-->

```{r include=FALSE, cache=FALSE}
set.seed(1014)
options(digits = 3)

###############################################################################
## setup
###############################################################################
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = TRUE,
  fig.retina = 0.8, # figures are either vectors or 300 dpi diagrams
  dpi = 300,
  out.width = "70%",
  fig.align = 'center',
  fig.width = 6,
  fig.asp = 0.618,  # 1 / phi
  fig.show = "hold",
  eval.after = 'fig.cap' # so captions can use link to demos
)

options(dplyr.print_min = 6,
        dplyr.print_max = 6,
        knitr.graphics.auto_pdf = TRUE)
```
# Results


<!--chapter:end:results.Rmd-->

```{r include=FALSE, cache=FALSE}
set.seed(1014)
options(digits = 3)

###############################################################################
## setup
###############################################################################
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = TRUE,
  fig.retina = 0.8, # figures are either vectors or 300 dpi diagrams
  dpi = 300,
  out.width = "70%",
  fig.align = 'center',
  fig.width = 6,
  fig.asp = 0.618,  # 1 / phi
  fig.show = "hold",
  eval.after = 'fig.cap' # so captions can use link to demos
)

options(dplyr.print_min = 6,
        dplyr.print_max = 6,
        knitr.graphics.auto_pdf = TRUE)
```
# Discussion

<!--chapter:end:discussion.Rmd-->

```{r include=FALSE, cache=FALSE}
set.seed(1014)
options(digits = 3)

###############################################################################
## setup
###############################################################################
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = TRUE,
  fig.retina = 0.8, # figures are either vectors or 300 dpi diagrams
  dpi = 300,
  out.width = "70%",
  fig.align = 'center',
  fig.width = 6,
  fig.asp = 0.618,  # 1 / phi
  fig.show = "hold",
  eval.after = 'fig.cap' # so captions can use link to demos
)

options(dplyr.print_min = 6,
        dplyr.print_max = 6,
        knitr.graphics.auto_pdf = TRUE)
```
# References

<div id="refs"></div>


<!--chapter:end:references.Rmd-->

```{r include=FALSE, cache=FALSE}
set.seed(1014)
options(digits = 3)

###############################################################################
## setup
###############################################################################
knitr::opts_chunk$set(
  comment = "#>",
  collapse = TRUE,
  cache = TRUE,
  fig.retina = 0.8, # figures are either vectors or 300 dpi diagrams
  dpi = 300,
  out.width = "70%",
  fig.align = 'center',
  fig.width = 6,
  fig.asp = 0.618,  # 1 / phi
  fig.show = "hold",
  eval.after = 'fig.cap' # so captions can use link to demos
)

options(dplyr.print_min = 6,
        dplyr.print_max = 6,
        knitr.graphics.auto_pdf = TRUE)
```
# (PART) Appendix {-}

# Notes


<!--chapter:end:notes.Rmd-->

